\documentclass [11pt]{article}
\usepackage{setspace,amssymb,latexsym,amsmath,amscd,epsfig,amsthm,wasysym,url}

\font\minihelv=phvr at 6pt
\font\helv=phvr at 10pt
\font\bighelv=phvr at 20pt
\font\hugehelv=phvr at 36pt
\font\mybigfont=phvr at 16pt
\font\mymediumfont=phvr at 14pt
\font\mediumhelv=phvr at 14pt
\font\mybfit=ptmbi at 12pt

\def\minivskip{\vskip 1.5mm}
\def\myspace{\phantom{\Biggr\|}}
\def\leavespace{\vskip 4mm}

\def\cosec{\hbox{cosec}}
\def\sec{\hbox{sec}}
\def\cotan{\hbox{cotan}}

\parindent=0pt
\setlength{\evensidemargin}{0.0cm}
\setlength{\oddsidemargin}{0.0cm}
\setlength{\topmargin}{-1.5cm}
%\setlength{\baselineskip}{20pt}
\setlength{\textwidth}{17cm}
\setlength{\textheight}{23.5cm}
\hoffset = -0.25cm



\begin{document}

   \begin{center}

     {\helv Hamilton College, Department of Government} \\
     {\bighelv Government 117W.03 \& 04 -- Fall 2013} \\
     {\mediumhelv Introduction to Political Theory} \\
     \ \\
     \ \\

     \begin{tabular}{ l r }

       \begin{tabular}{l}
          Instructor: Joel Winkelman           \\
          Office: KJ137                  \\
          E-mail: {\tt jwinkelm@hamilton.edu}     \\
          Twitter: {\tt @joelwinkelman} \\
          Office Phone: \tt{x4984}         \\
                                            \\
       \end{tabular}

       &

       \begin{tabular}{l}
          Class: 03, MW 1--2:15pm, KJ104 \\
          \phantom{Class: }04, MW 2--3:30pm, KJ203 \\
          Office Hours: MW 3:30--4:30pm, R 9--10am \\
          \phantom{Office Hours: }and by appointment                \\
                                            \\
                                            \\
       \end{tabular}

     \end{tabular}

   \end{center}

   \ \\

   {\bf Course introduction and goals} \\
   ``Guesses, with persons left to themselves, tend to become opinions, and opinions dogmas. To hold theories and principles in solution, awaiting confirmation, goes contrary to the grain. Even today questioning a statement made by a person is often taken by him as a reflection upon his integrity, and is resented.'' ---John Dewey, \textit{Freedom and Culture} \\

   Political theory is the study of the ideas, principles, and concepts that inform political life. The primary goal of the course is to introduce the most important and enduring problems in political life. We will develop the analytical skills necessary to do more than simply guess, preventing opinions from becoming dogma by asking questions not only of one another, but also---and especially---of ourselves. In particular, we will consider questions about who should rule, the meaning of justice, and the scope of political authority. This course assumes that any answer to these questions depends on an account of what it means to be human, the discovery and analysis of which is one of our main tasks. Our method will be to explore the thought of a selection of thinkers across history, from Ancient Greece to the 20th-century United States. \\


   {\bf Required Reading}\\

All texts available at the College Store. Please refer to ISBN numbers if purchasing from another source. Page numbers on the syllabus will correspond to these editions. While I have made every effort to order inexpensive editions of the texts, an equally important criterion was inclusion and quality of bibliographic, introductory, and other supplemental essays, which are valuable resources for your written assignments. \\

   Sophocles, Theban Plays (Hackett) [9780872205857] \\ % 1 day each/play
   Plato, Republic (Hackett) \{C.D.C. Reeve, trans.\} [9780872207363] \\ % [3 days??] day 1: book 1; day 2: 368c--383c, 412b--417b, 
   Machiavelli, The Prince (Oxford World's Classics) [9780199535699] \\ % chs. 1--13 (day 1), 14--26 (day 2)
   Montesquieu, Persian Letters (Oxford World's Classics) [9780192806352] \\ % 
   Rousseau, A Discourse on Inequality (Penguin Classics) [9780140444391] \\ % day 1: roughly 55--97; day 2: 98--139
   Mill, Essays on Sex Equality (Chicago) [9780226525464] \\ % day 1: 123--182; day 2: 183--242
   Marx, The Communist Manifesto: A Modern Edition (Verso) [9781844678761] \\ % day 1: 31--79
   Du Bois, The Souls of Black Folk (Oxford World's Classics) [9780199555833] \\ % 
   \ \\
\vfill\eject
   {\bf Course Requirements}\\
\\
\emph{Preparation and participation.} This course will be conducted as a seminar. I will provide some basic historical, biographical, or interpretive background for each thinker, but class will be primarily discussion-based. Thus success in this course demands your active preparation and participation. For our purposes, preparation includes not only reading, but also reflecting on the assigned reading. I will call on students. If students regularly are not prepared, I will use reading quizzes as an incentive for preparation. \\

\emph{Papers.} This course is Writing-Intensive (WI). Because learning to write well is an on-going process, the faculty has committed to a WI Program that will assist students in learning to write well in multiple disciplines and throughout their time at Hamilton. As a designated WI course, the formal written requirements for the course will consist of three short essays, one peer review, and a research paper. The writing process will include early drafts and revisions, with feedback from peers and the instructor. Sixty-five (65) percent of your grade is determined by written assignments. Please refer to specific assignments for details such as due dates, expectations for revision, assignment length, etc.\\

\emph{Panel discussions.} Students will participate in one of four panel discussions moderated by the instructor. You will be responsible for a 12-minute presentation, and a short question-and-answer period. Your presentation will be based on one of your papers.\\

\emph{Final exam.} The cumulative final exam will be closed book and will consist of identification, and short answer questions. \\

Final grades will be determined according to the following rubric: \\
\ \\
\begin{tabular}{ l r }
\hline
  {\bf Assignment}                     & Percentage  \\
                      
\hline \hline

\emph{Participation and preparation}           & 20 \\
                          
\emph{First Essay (Original)}                  & 5  \\
                                                   
\emph{First Essay (Revised)}                   & 10 \\                      

\emph{Second Essay}                            & 15 \\
                          
\emph{Third Essay}                             & 13 \\
                                         
\emph{Peer Review (of Third Essay)}            & 2  \\
                      
\emph{Research Paper (Draft)}                  & 5  \\
                          
\emph{Research Paper (Final)}                  & 15 \\
                                                               
\emph{Panel Discussion}                        & 5  \\
     
\emph{Final Exam}                              & 10 \\
                          
\hline
Total                                          & 100 \\
\hline
\end{tabular} \\

\ \\
   {\bf Class Conduct and Expectations}\\

No incompletes, extensions, or makeups will be given, nor any absences excused, without legitimate justification (e.g., verifiable medical illness).  Documentation will be required in all cases and the instructor must be notified in advance. Students also are responsible for making computer backup files of all course work. \\

All students are expected to abide by the Hamilton College Honor Code. A copy of the honor code can be found at: {\tt http://www.hamilton.edu/student-handbook/studentconduct/honor-code}. \\

Unless you have a documented disability that requires use of a laptop in class, all personal electronic devices must be silenced and put away while in class. If you are texting or using an electronic device without authorization during class, you will be marked as absent for the day. \\

[Notice: Hamilton College will make reasonable accommodations for students with properly documented disabilities.  If you are eligible to receive an accommodation(s) and would like to make a formal request for this course, please be certain to discuss it with me during the first two weeks of class.  You will need to provide Allen Harrison, Associate Dean of Students (Elihu Root House; ext. 4021) with appropriate documentation of your disability.]

\ \\

%% Schedule

   {\bf  Course Schedule}\\


\noindent
Mon, September 2 -- Course introduction \\

\noindent
Wed, September 4 -- Action and Recognition \\
\phantom{Wed, September 4 -- }Sophocles, \textit{Antigone} (entire). \\

\noindent
Mon, September 9 -- Identity and Human Nature \\
\phantom{Mon, September 9 -- }Sophocles, \textit{Oedipus Tyrannus} (entire). \\

\noindent
Wed, September 11 -- Socrates and the Purpose of Politics  \\
\phantom{Wed, September 11 -- }Plato, \textit{Republic}, Book 1. \\

\noindent
Mon, September 16 -- Plato and the Purpose of Philosophy \\
\phantom{Mon, September 16 -- }Plato, \textit{Republic}, Book 2. \\
\phantom{Mon, September 16 -- }\textbf{Original First Paper Due} by 11:59pm. \\

\noindent
Wed, September 18 -- The Soul and the City \\
\phantom{Wed, September 18 -- }Plato, \textit{Republic}, Book 4. \\ 

\noindent
Mon, September 23 -- The Cave and the King \\
\phantom{Mon, September 23 -- }Plato, \textit{Republic}, Book 7. \\
\phantom{Mon, September 23 -- }\textbf{Revised First Paper Due} by 11:59pm. \\

\noindent
Wed, September 25 -- The Prince and Power \\
\phantom{Wed, September 25 -- }Machiavelli, \textit{The Prince}, chs. 1--7.  \\

\noindent
Mon, September 30 -- The Prince and the People \\
\phantom{Mon, September 30 -- }Machiavelli, \textit{The Prince}, chs. 8--18. \\

\noindent
Wed, October 2 -- Fortune and \emph{virt\`u} \\
\phantom{Wed, October 2 -- }Machiavelli, \textit{The Prince}, chs. 19--26.\\

\noindent
Mon, October 7 -- \textbf{First Panel Discussion} \\
\phantom{Mon, October 7 -- }No reading. \\

\noindent
Wed, October 9 -- Authenticity and Authority \\ 
\phantom{Wed, October 9 -- }Montesquieu, \textit{Persian Letters}, pp. 3--42. \\

\noindent
Mon, October 14 -- Love and Freedom \\
\phantom{Mon, October 14 -- }Montesquieu, \textit{Persian Letters}, \#s 32, 36, 51, 53, 62--63, 65, 76, 78; SL 8. \\
\phantom{Mon, October 14 -- }\textbf{Second Paper Due} by 11:59pm. \\

\noindent
Wed, October 16 --  Gender and Genre \\ 
\phantom{Wed, October 16 -- }Montesquieu, \textit{Persian Letters}, \#s  84, 87, 88, 93, 120, 135, 139--150. \\

\noindent
Mon, October 21 -- Natural Man and the Origin of Society \\
\phantom{Mon, October 21 -- }Rousseau, \textit{Discourse on Inequality}, pp. 55--97.\\

\noindent
Wed, October 23 -- Inequality and Civil Society  \\
\phantom{Mon, October 23 -- }Rousseau, \textit{Discourse on Inequality}, pp. 98--139.\\

\noindent
Wed, October 28 -- \textbf{Second Panel Discussion} \\
\phantom{Wed, October 28 -- }No reading. \\

\noindent
Wed, October 30 -- Marxism and Revolution \\
\phantom{Wed, October 30 -- }Marx, \textit{The Communist Manifesto}, pts. 1 \& 2. \\

\noindent
Mon, November 4 -- Communism, Class, and History \\
\phantom{Mon, November 4 -- }Marx, \textit{The Communist Manifesto}, pts. 3 \& 4. \\

Wed, November 6 -- \textbf{Peer Review} \\
\phantom{Wed, November 6 -- }No reading. \\
\phantom{Wed, November 6 -- }\textbf{Draft of Third Paper due}. \\

\noindent
Mon, November 11 -- Woman Suffrage \\
\phantom{Mon, November 11 -- }Harriet Taylor Mill, ``Enfranchisement of Women,'' pp. 89--122. \\
\phantom{Mon, November 11 -- }\textbf{Third Paper Due} \\

\noindent
Wed, November 13 -- Sex Equality \\
\phantom{Wed, November 13 -- }Mill, ``On the Subjection of Women,'' pgs. 123--182. \\

\noindent
Mon, November 18 -- Marriage Equality \\
\phantom{Mon, November 18 -- }Mill, ``On the Subjection of Women,'' pgs. 183--242. \\

\noindent
Wed, November 20 -- \textbf{Third Panel Discussion} \\
\phantom{Wed, November 20 -- }No reading. \\

\noindent
Mon, December 2 -- The Color Line \\
\phantom{Mon, December 2 -- }DuBois, \textit{The Souls of Black Folk}, Forethought \& chs. 1--3. \\
\phantom{Mon, December 2 -- }\textbf{Draft Research Paper Due} \\

\noindent
Wed, December 4 -- Labor and Culture \\
\phantom{Wed, December 4 -- }DuBois, \textit{The Souls of Black Folk}, chs. 6, 8--9. \\

\noindent
Mon, December 9 -- Education and Tragedy \\
\phantom{Mon, December 9 -- }DuBois, \textit{The Souls of Black Folk}, chs. 12--14 \& Afterthought. \\

\noindent
Wed, December 11 -- \textbf{Fourth Panel Discussion} \\
\phantom{Wed, December 11 -- }\textbf{Final Research Paper Due} \\
\phantom{Wed, December 11 -- }No reading. \\

\textbf{Wed, December 18, 9am -- Final Exam.}

\end{document}
